G85R Analysis: Rescue Response

### 2024-11-06 TKT_RNAseq/R Code/TKT-OE_RNAseqRescueResponse.Rmd
pca

x = "GRxWT.FC"
y = "GRxWT.MC"

mean.data = G85R.meancpm[, c('WT.F', 'WT.M',
                             'GR.F', 'GR.M')]
main.title = "G85R vs WT: Female and Male DE Genes"

##RG = Response Genes
GRxWT.RG = TKT.biplot(x, y, mean.data, main.title)

GRxWT.RG[[1]]

@@

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] > 0, "FBgn"]
s2 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] < 0, "FBgn"]
s3 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] > 0, "FBgn"]
s4 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] < 0, "FBgn"]

@@

par(mar = c(2,4,2,7.5))
barplot(NormalResponse,
        beside = T,
        ylab = "Total DEGs",
        main = "G85R vs Silent",
        col = c('navy', 'firebrick'),
        angle = c(45, 45, 315, 315), density = 50,
        legend.text = c("Decreased", "Increased"),
        args.legend = list(x = 8,
                           y = 700,
                           bty = 'n'))
#legend(x = 6.25, 
#       y = 700, 
#       legend = c("Increased", "Decreased"),
#       pt.bg = c('grey35', 'lightgrey'),
#       xpd = T, 
#       bty = "o",
#       pch = 22,
#       pt.cex = 1.5)

@@

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s3 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] > 0, "FBgn"]
s1 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] < 0, "FBgn"]
s4 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] > 0, "FBgn"]
s2 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] < 0, "FBgn"]

@@

s1 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] > 0, "FBgn"]
s2 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] < 0, "FBgn"]
s3 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] > 0, "FBgn"]
s4 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] < 0, "FBgn"]

@@

bg = row.names(TKT.EdgeR)
GRWTMF.Enr = Subset.Enrichment(bg, MF.shared.DEGs)

RTCC.GRWTMF = tree(GRWTMF.Enr, "CC")
treemapPlot(RTCC.GRWTMF)

RTCC.GRWTMF = tree(GRWTMF.Enr, "BP")
treemapPlot(RTCC.GRWTMF)

RTCC.GRWTMF = tree(GRWTMF.Enr, "MF")
treemapPlot(RTCC.GRWTMF)

cat.data = GRWTMF.Enr
GO.ontology = "CC"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = "sigs.only"
sigs = MF.shared.DEGs

cat.data = GRWTMF.Enr
GO.ontology = "BP"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = c(1:39)
sigs = MF.shared.DEGs

cat.data = GRWTMF.Enr
GO.ontology = "MF"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = c(1:30)
sigs = MF.shared.DEGs

@@

F.only.DEGs = c(setdiff(GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05, "FBgn"],
                        GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]))

bg = row.names(TKT.EdgeR)
GRWTFonly.Enr = Subset.Enrichment(bg, F.only.DEGs)

RTCC.GRWTFonly = tree(GRWTFonly.Enr, "CC")
treemapPlot(RTCC.GRWTFonly)

RTCC.GRWTFonly = tree(GRWTFonly.Enr, "BP")
treemapPlot(RTCC.GRWTFonly)

RTCC.GRWTFonly = tree(GRWTFonly.Enr, "MF")
treemapPlot(RTCC.GRWTFonly)
```

cat.data = GRWTFonly.Enr
GO.ontology = "CC"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = "sigs.only"
sigs = F.only.DEGs

cat.data = GRWTFonly.Enr
GO.ontology = "BP"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = "sigs.only"
sigs = F.only.DEGs

cat.data = GRWTFonly.Enr
GO.ontology = "MF"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = "sigs.only"
sigs = F.only.DEGs

@@

M.only.DEGs = c(setdiff(GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05, "FBgn"],
                        GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]))

bg = row.names(TKT.EdgeR)
GRWTMonly.Enr = Subset.Enrichment(bg, M.only.DEGs)
```

RTCC.GRWTMonly = tree(GRWTMonly.Enr, "CC")
treemapPlot(RTCC.GRWTMonly)

@@

RTCC.GRWTMonly = tree(GRWTMonly.Enr, "BP")
treemapPlot(RTCC.GRWTMonly)

@@

RTCC.GRWTMonly = tree(GRWTMonly.Enr, "MF")
treemapPlot(RTCC.GRWTMonly)

>>>>

mean.data = G85R.meancpm[, c('GR.F', 'GR.M',
                             'TktOEGR.F', 'TktOEGR.M')]
main.title = "G85R Control vs TKT-OE: Female and Male DE Genes"

##RG = Response Genes
GR.CxOE.RG = TKT.biplot(x, y, mean.data, main.title)

GR.CxOE.RG[[1]]

@@

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05 &
                     GR.CxOE.RG[[2]][,'FC1'] > 0, "FBgn"]
s2 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05 &
                     GR.CxOE.RG[[2]][,'FC1'] < 0, "FBgn"]
s3 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05 &
                     GR.CxOE.RG[[2]][,'FC2'] > 0, "FBgn"]
s4 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05 &
                     GR.CxOE.RG[[2]][,'FC2'] < 0, "FBgn"]

@@

par(mar = c(2,4,2,7.5))
barplot(NormalResponse,
        beside = T,
        ylab = "Total DEGs",
        main = "G85R Control vs TKT-OE",
        col = c('navy', 'firebrick'),
        angle = c(45, 45, 315, 315), density = 50,
        legend.text = c("Decreased", "Increased"),
        args.legend = list(x = 8,
                           y = 700,
                           bty = 'n'))
#legend(x = 6.25, 
#       y = 700, 
#       legend = c("Increased", "Decreased"),
#       pt.bg = c('grey35', 'lightgrey'),
#       xpd = T, 
#       bty = "o",
#       pch = 22,
#       pt.cex = 1.5)

@@

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s3 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05 &
                     GR.CxOE.RG[[2]][,'FC1'] > 0, "FBgn"]
s1 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05 &
                     GR.CxOE.RG[[2]][,'FC1'] < 0, "FBgn"]
s4 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05 &
                     GR.CxOE.RG[[2]][,'FC2'] > 0, "FBgn"]
s2 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05 &
                     GR.CxOE.RG[[2]][,'FC2'] < 0, "FBgn"]

@@

s1 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05 &
                     GR.CxOE.RG[[2]][,'FC1'] > 0, "FBgn"]
s2 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05 &
                     GR.CxOE.RG[[2]][,'FC1'] < 0, "FBgn"]
s3 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05 &
                     GR.CxOE.RG[[2]][,'FC2'] > 0, "FBgn"]
s4 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05 &
                     GR.CxOE.RG[[2]][,'FC2'] < 0, "FBgn"]

@@

bg = row.names(TKT.EdgeR)
GR.CxOE.MF.Enr = Subset.Enrichment(bg, MF.shared.DEGs)

@@

F.only.DEGs = c(setdiff(GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05, "FBgn"],
                        GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]))

bg = row.names(TKT.EdgeR)
GR.CxOE.Fonly.Enr = Subset.Enrichment(bg, F.only.DEGs)

@@

M.only.DEGs = c(setdiff(GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05, "FBgn"],
                        GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]))

bg = row.names(TKT.EdgeR)
GR.CxOE.Monly.Enr = Subset.Enrichment(bg, M.only.DEGs)

@@

##no significantly enriched GO terms in sex independent or sex dependent DEG sets

##All Female DEGs

F.DEGs = c(GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05, "FBgn"])

bg = row.names(TKT.EdgeR)
GR.CxOE.F.Enr = Subset.Enrichment(bg, F.DEGs)

@@

RTCC.GR.CxOE.F = tree(GR.CxOE.F.Enr, "CC")
treemapPlot(RTCC.GR.CxOE.F)
